\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2011-04-08 doc/USER_MANUAL/manual_SPECFEM3D.tex
updates source code headers; updates package version number to version 2.0.1

The SPECFEM3D software package comes in a gzipped tar ball. In the
directory in which you want to install the package, type
\begin{lyxcode}
{\small tar~-zxvf~SPECFEM3D\_V2.0.0.tar.gz}{\small \par}
\end{lyxcode}
The directory \texttt{\small SPECFEM3D/} will then contain
the source code. To configure the software for your system, run the
\texttt{configure} shell script. This script will attempt to guess
the appropriate configuration values for your system. However, at
a minimum, it is recommended that you explicitly specify the appropriate
command names for your Fortran90 compiler and MPI package:

@@

$\copyright$ Princeton University and University of Pau / CNRS / INRIA, November 2010

>>>>

The SPECFEM3D software package comes in a gzipped tar ball. In the
directory in which you want to install the package, type
\begin{lyxcode}
{\small tar~-zxvf~SPECFEM3D\_V2.0.1.tar.gz}{\small \par}
\end{lyxcode}
The directory \texttt{\small SPECFEM3D/} will then contain
the source code. To configure the software for your system, run the
\texttt{configure} shell script. This script will attempt to guess
the appropriate configuration values for your system. However, at
a minimum, it is recommended that you explicitly specify the appropriate
command names for your Fortran90 compiler and MPI package:

@@

$\copyright$ Princeton University and University of Pau / CNRS / INRIA, April 2011
